Re-analysing the data from Moffatt et al. (\protect\hyperlink{ref-moffatt_inner_2020}{2020}): A textbook illustration of the absence of evidence fallacy

### 2020-09-29 reanalysis.Rmd
minor updates in readme

# setting seed for reproducibility
set.seed(666)

# setting up knitr options
knitr::opts_chunk$set(
  cache = TRUE, eval = TRUE, echo = FALSE,
  warning = FALSE, message = FALSE,
  fig.align = "center", dev = "pdf",
  out.width = "100%", fig.pos = "!htb"
  )

@@

# plotting the data
df2 %>%
    # reshapes data from wide to long format
    pivot_longer(
        cols = FRO:OOI,
        names_to = "muscle",
        values_to = "value",
        values_drop_na = TRUE
        ) %>%
    mutate(order = factor(order) ) %>%
    # plots the data
    ggplot(aes(x = condition, y = value) ) +
    # violin plots
    geom_violin(
        scale = "count",
        fill = "black",
        alpha = 0.15,
        colour = "white",
        position = pd,
        # adjust = 0.8,
        draw_quantiles = 0.5,
        show.legend = FALSE
        ) +
    # plotting individual data points
    # geom_dotplot(
    #     stackdir = "center",
    #     binaxis = "y",
    #     position = pd,
    #     # binwidth = 1,
    #     dotsize = 0.5,
    #     alpha = 0.3
    #     ) +
    geom_quasirandom(alpha = 0.3) +
    stat_summary(
        fun.y = mean,
        geom = "line", size = 1,
        # aes(group = interaction(muscle, order) ),
        aes(group = muscle),
        position = pd,
        show.legend = FALSE
        ) +
    # plotting means
    stat_summary(
        fun.y = "mean",
        geom = "point", shape = 16, size = 3,
        position = pd,
        show.legend = TRUE
        ) +
    # plotting confidence intervals
    stat_summary(
        fun.data = mean_cl_normal,
        geom = "errorbar", size = 1, width = 0,
        fun.args = list(mult = 1.96),
        show.legend = FALSE,
        position = pd
        ) +
    # facet_wrap(~order*muscle, ncol = 3) +
    facet_wrap(~muscle, ncol = 3) +
    labs(x = "Condition", y = "Natural logarithm of peak amplitude") +
    theme_bw(base_size = 12) +
    scale_colour_brewer(palette = "Dark2", direction = 1) +
    scale_fill_brewer(palette = "Dark2", direction = 1)
```

@@

@@

```{r simulated-power, fig.width = 10, fig.cap = "Average natural logarithm of the Bayes factor in favour of the alternative hypothesis (BF10), along with its standard error, computed over 1000 datasets of increasing size simulated from the posterior predictive distribution of the varying-intercept multivariate Bayesian regresion model."}
# running the simulations
# source("code/bf_simulation.R")

@@

# plotting the results
overall_results %>%
    na.omit() %>%
    filter_all(any_vars(. != 0) ) %>%
    pivot_longer(cols = bf_fro:bf_oos, names_to = "bf_type") %>%
    mutate(value = log(value) ) %>%
    mutate(bf_type = factor(bf_type, labels = c("FRO", "OOI", "OOS") ) ) %>%
    group_by(nobs, bf_type) %>%
    summarise(
        across(
            .cols = value,
            .fns = list(mean = mean, median = median, se = ~sd(.x) / sqrt(nsims), mad = mad)
            )
        ) %>%
    ungroup() %>%
    ggplot(aes(x = nobs, y = value_mean, colour = bf_type, fill = bf_type) ) +
    geom_hline(yintercept = 0, lty = 3) +
    geom_ribbon(
        aes(x = nobs, ymin = value_mean - 1.96 * value_se, ymax = value_mean + 1.96 * value_se, colour = NULL),
        # aes(x = nobs, ymin = value_median - value_mad, ymax = value_median + value_mad, colour = NULL),
        alpha = 0.5, show.legend = FALSE
        ) + 
    geom_line(show.legend = FALSE) +
    # geom_line(aes(y = value_median), show.legend = FALSE) +
    geom_point(show.legend = FALSE) +
    facet_wrap(~bf_type, scales = "free") +
    scale_x_continuous(breaks = unique(sample_size) ) +
    theme_bw(base_size = 12) +
    labs(x = "Number of participants", y = "Natural logarithm of the Bayes factor") +
    scale_colour_brewer(palette = "Dark2", direction = 1) +
    scale_fill_brewer(palette = "Dark2", direction = 1)
```

@@

# plotting the data
df2 %>%
    # reshapes data from wide to long format
    pivot_longer(
        cols = FRO:OOI,
        names_to = "muscle",
        values_to = "value",
        values_drop_na = TRUE
        ) %>%
    mutate(order = factor(order, labels = c("RUM -> DIS", "DIS -> RUM")) ) %>%
    # plots the data
    ggplot(aes(x = condition, y = value, colour = order, fill = order) ) +
    # plotting individual data points
    geom_quasirandom(alpha = 0.3) +
    # plotting means
    stat_summary(
        fun.y = mean,
        geom = "line", size = 1,
        aes(group = interaction(muscle, order) ),
        # aes(group = muscle),
        position = pd,
        show.legend = FALSE
        ) +
    # plotting means
    stat_summary(
        fun.y = "mean",
        geom = "point", shape = 16, size = 3,
        position = pd,
        show.legend = TRUE
        ) +
    # plotting confidence intervals
    stat_summary(
        fun.data = mean_cl_normal,
        geom = "errorbar", size = 1, width = 0,
        fun.args = list(mult = 1.96),
        show.legend = FALSE,
        position = pd
        ) +
    # facetting by muscle
    facet_wrap(~muscle, ncol = 3) +
    labs(x = "Condition", y = "Natural logarithm of peak amplitude") +
    theme_bw(base_size = 12) +
    scale_colour_brewer(palette = "Dark2", direction = 1) +
    scale_fill_brewer(palette = "Dark2", direction = 1) +
    theme(
      legend.title = element_blank(),
      # legend.position = c(0.85, 0.85),
      legend.position = "top",
      legend.background = element_rect(size = 0.5, linetype = "solid", colour = "black")
    )
```

@@

```{r everyone, fig.cap = "Inter-individual variability in the main effect of interest (i.e., the difference between the rumination and distraction conditions). Green dots and lines represent the average logarithm of the EMG amplitude of participants that showed a higher EMG amplitude in the rumination condition than in the distraction condition, whereas orange dots and lines represent the average logarithm of the EMG amplitude of participants that showed a higher EMG amplitude in the distraction condition than in the rumination condition."}
# does everyone plot
df2 %>%
    pivot_longer(cols = FRO:OOI, names_to = "muscle") %>%
    pivot_wider(names_from = condition, values_from = value) %>%
    mutate(ruminator = ifelse(RUM > DIS, 1, 0) ) %>%
    mutate(ruminator = as.factor(ruminator) ) %>%
    pivot_longer(cols = RUM:BAS, names_to = "condition") %>%
    ggplot(aes(x = condition, y = value, colour = ruminator, fill = ruminator) ) +
    # violin plots
    geom_violin(
        scale = "count",
        fill = "black",
        alpha = 0.15,
        colour = "white",
        position = pd,
        # adjust = 0.8,
        draw_quantiles = 0.5,
        show.legend = FALSE
        ) +
    # plotting individual data points
    # geom_quasirandom(alpha = 0.3) +
    geom_point(size = 2, alpha = 0.8, show.legend = FALSE) +
    geom_line(aes(group = ID), size = 0.5, alpha = 0.8, show.legend = FALSE) +
    # plitting the by-group mean
    # stat_summary(
    #     fun.y = mean,
    #     geom = "line", size = 2,
    #     aes(group = interaction(muscle, ruminator) ),
    #     position = pd,
    #     show.legend = FALSE
    #     ) +
    # plotting means
    # stat_summary(
    #     fun.y = "mean",
    #     geom = "point", shape = 16, size = 4,
    #     position = pd,
    #     show.legend = TRUE
    #     ) +
    # plotting confidence intervals
    # stat_summary(
    #     fun.data = mean_cl_normal,
    #     geom = "errorbar", size = 2, width = 0,
    #     fun.args = list(mult = 1.96),
    #     show.legend = FALSE,
    #     position = pd
    #     ) +
    # facetting by muscle
    facet_wrap(~muscle) +
    # axis labels
    labs(x = "Condition", y = "Natural logarithm of peak amplitude") +
    theme_bw(base_size = 12) +
    scale_colour_brewer(palette = "Dark2", direction = -1) +
    scale_fill_brewer(palette = "Dark2", direction = -1)
```

>>>>

# setting seed for reproducibility
# set.seed(666)

# setting up knitr options
knitr::opts_chunk$set(
  cache = TRUE, eval = TRUE, echo = FALSE,
  warning = FALSE, message = FALSE,
  fig.align = "center", dev = "pdf",
  out.width = "100%", fig.width = 8,
  fig.pos = "!htb"
  )

@@

# plotting the data
df2 %>%
    # reshapes data from wide to long format
    pivot_longer(
        cols = FRO:OOI,
        names_to = "muscle",
        values_to = "value",
        values_drop_na = TRUE
        ) %>%
    mutate(order = factor(order) ) %>%
    # plots the data
    ggplot(aes(x = condition, y = value) ) +
    # violin plots
    geom_violin(
        scale = "count",
        fill = "black",
        alpha = 0.15,
        colour = "white",
        position = pd,
        # adjust = 0.8,
        draw_quantiles = 0.5,
        show.legend = FALSE
        ) +
    # plotting individual data points
    # geom_dotplot(
    #     stackdir = "center",
    #     binaxis = "y",
    #     position = pd,
    #     # binwidth = 1,
    #     dotsize = 0.5,
    #     alpha = 0.3
    #     ) +
    geom_quasirandom(alpha = 0.3) +
    stat_summary(
        fun.y = mean,
        geom = "line", size = 1,
        # aes(group = interaction(muscle, order) ),
        aes(group = muscle),
        position = pd,
        show.legend = FALSE
        ) +
    # plotting means
    stat_summary(
        fun.y = "mean",
        geom = "point", shape = 16, size = 3,
        position = pd,
        show.legend = TRUE
        ) +
    # plotting confidence intervals
    stat_summary(
        fun.data = mean_cl_normal,
        geom = "errorbar", size = 1, width = 0,
        fun.args = list(mult = 1.96),
        show.legend = FALSE,
        position = pd
        ) +
    # facet_wrap(~order*muscle, ncol = 3) +
    facet_wrap(~muscle, ncol = 3) +
    labs(x = "Condition", y = "Natural logarithm of peak amplitude") +
    theme_bw(base_size = 10) +
    scale_colour_brewer(palette = "Dark2", direction = 1) +
    scale_fill_brewer(palette = "Dark2", direction = 1)
```

@@

```{r model, eval = FALSE, results = "hide"}
# priors for the varying-effects model
priors_varying <- c(
    prior(normal(0, 10), class = Intercept, resp = "FRO"),
    prior(normal(0, 1), class = b, resp = "FRO"),
    prior(exponential(1), class = sigma, resp = "FRO"),
    prior(exponential(1), class = sd, resp = "FRO"),
    prior(normal(0, 10), class = Intercept, resp = "OOS"),
    prior(normal(0, 1), class = b, resp = "OOS"),
    prior(exponential(1), class = sigma, resp = "OOS"),
    prior(exponential(1), class = sd, resp = "OOS"),
    prior(normal(0, 10), class = Intercept, resp = "OOI"),
    prior(normal(0, 1), class = b, resp = "OOI"),
    prior(exponential(1), class = sigma, resp = "OOI"),
    prior(exponential(1), class = sd, resp = "OOI")
    )

# fitting the model
varying_effects <- brm(
    mvbind(FRO, OOS, OOI) ~ 1 + condition + (1 | ID),
    family = gaussian(),
    prior = priors_varying,
    data = df2,
    chains = 4, cores = detectCores(),
    warmup = 2000, iter = 10000,
    control = list(adapt_delta = 0.95),
    sample_prior = TRUE,
    file = here("models/varying_effects")
    )
```

Posterior distribution of the difference between the distraction and rumination conditions...

@@

```{r simulated-power, fig.cap = "Average natural logarithm of the Bayes factor in favour of the alternative hypothesis (BF10), along with its standard error, computed over 1000 datasets of increasing size simulated from the posterior predictive distribution of the varying-intercept multivariate Bayesian regresion model."}
# running the simulations
# source("code/bf_simulation.R")

@@

# plotting the results
overall_results %>%
    na.omit() %>%
    filter_all(any_vars(. != 0) ) %>%
    pivot_longer(cols = bf_fro:bf_oos, names_to = "bf_type") %>%
    mutate(value = log(value) ) %>%
    mutate(bf_type = factor(bf_type, labels = c("FRO", "OOI", "OOS") ) ) %>%
    group_by(nobs, bf_type) %>%
    summarise(
        across(
            .cols = value,
            .fns = list(mean = mean, median = median, se = ~sd(.x) / sqrt(nsims), mad = mad)
            )
        ) %>%
    ungroup() %>%
    ggplot(aes(x = nobs, y = value_mean, colour = bf_type, fill = bf_type) ) +
    geom_hline(yintercept = 0, lty = 3) +
    geom_ribbon(
        aes(x = nobs, ymin = value_mean - 1.96 * value_se, ymax = value_mean + 1.96 * value_se, colour = NULL),
        # aes(x = nobs, ymin = value_median - value_mad, ymax = value_median + value_mad, colour = NULL),
        alpha = 0.5, show.legend = FALSE
        ) + 
    geom_line(show.legend = FALSE) +
    # geom_line(aes(y = value_median), show.legend = FALSE) +
    geom_point(show.legend = FALSE) +
    facet_wrap(~bf_type, scales = "free") +
    scale_x_continuous(breaks = unique(sample_size) ) +
    theme_bw(base_size = 10) +
    labs(x = "Number of participants", y = "Natural logarithm of the Bayes factor") +
    scale_colour_brewer(palette = "Dark2", direction = 1) +
    scale_fill_brewer(palette = "Dark2", direction = 1)
```

@@

# plotting the data
df2 %>%
    # reshapes data from wide to long format
    pivot_longer(
        cols = FRO:OOI,
        names_to = "muscle",
        values_to = "value",
        values_drop_na = TRUE
        ) %>%
    mutate(order = factor(order, labels = c("RUM -> DIS", "DIS -> RUM")) ) %>%
    # plots the data
    ggplot(aes(x = condition, y = value, colour = order, fill = order) ) +
    # plotting individual data points
    geom_quasirandom(alpha = 0.3) +
    # plotting means
    stat_summary(
        fun.y = mean,
        geom = "line", size = 1,
        aes(group = interaction(muscle, order) ),
        # aes(group = muscle),
        position = pd,
        show.legend = FALSE
        ) +
    # plotting means
    stat_summary(
        fun.y = "mean",
        geom = "point", shape = 16, size = 3,
        position = pd,
        show.legend = TRUE
        ) +
    # plotting confidence intervals
    stat_summary(
        fun.data = mean_cl_normal,
        geom = "errorbar", size = 1, width = 0,
        fun.args = list(mult = 1.96),
        show.legend = FALSE,
        position = pd
        ) +
    # facetting by muscle
    facet_wrap(~muscle, ncol = 3) +
    labs(x = "Condition", y = "Natural logarithm of peak amplitude") +
    theme_bw(base_size = 10) +
    scale_colour_brewer(palette = "Dark2", direction = 1) +
    scale_fill_brewer(palette = "Dark2", direction = 1) +
    theme(
      legend.title = element_blank(),
      # legend.position = c(0.85, 0.85),
      legend.position = "top",
      legend.background = element_rect(size = 0.5, linetype = "solid", colour = "black")
    )
```

@@

```{r everyone, fig.cap = "Inter-individual variability in the main effect of interest (i.e., the difference between the rumination and distraction conditions). Green dots and lines represent the average natural logarithm of the EMG amplitude of participants that showed a higher EMG amplitude in the rumination condition than in the distraction condition, whereas orange dots and lines represent the average natural logarithm of the EMG amplitude of participants that showed a higher EMG amplitude in the distraction condition than in the rumination condition."}
# does everyone plot
df2 %>%
    pivot_longer(cols = FRO:OOI, names_to = "muscle") %>%
    pivot_wider(names_from = condition, values_from = value) %>%
    mutate(ruminator = ifelse(RUM > DIS, 1, 0) ) %>%
    mutate(ruminator = as.factor(ruminator) ) %>%
    pivot_longer(cols = RUM:BAS, names_to = "condition") %>%
    ggplot(aes(x = condition, y = value, colour = ruminator, fill = ruminator) ) +
    # violin plots
    geom_violin(
        scale = "count",
        fill = "black",
        alpha = 0.15,
        colour = "white",
        position = pd,
        # adjust = 0.8,
        draw_quantiles = 0.5,
        show.legend = FALSE
        ) +
    # plotting individual data points
    geom_point(size = 2, alpha = 0.8, show.legend = FALSE) +
    # plotting individual trajectories
    geom_line(aes(group = ID), size = 0.5, alpha = 0.8, show.legend = FALSE) +
    # facetting by muscle
    facet_wrap(~muscle) +
    # axis labels
    labs(x = "Condition", y = "Natural logarithm of peak amplitude") +
    theme_bw(base_size = 10) +
    scale_colour_brewer(palette = "Dark2", direction = -1) +
    scale_fill_brewer(palette = "Dark2", direction = -1)
```

### 2020-09-29 reanalysis.tex
minor updates in readme

\caption{Inter-individual variability in the main effect of interest (i.e., the difference between the rumination and distraction conditions). Green dots and lines represent the average logarithm of the EMG amplitude of participants that showed a higher EMG amplitude in the rumination condition than in the distraction condition, whereas orange dots and lines represent the average logarithm of the EMG amplitude of participants that showed a higher EMG amplitude in the distraction condition than in the rumination condition.}\label{fig:everyone}
\end{figure}

>>>>

\caption{Inter-individual variability in the main effect of interest (i.e., the difference between the rumination and distraction conditions). Green dots and lines represent the average natural logarithm of the EMG amplitude of participants that showed a higher EMG amplitude in the rumination condition than in the distraction condition, whereas orange dots and lines represent the average natural logarithm of the EMG amplitude of participants that showed a higher EMG amplitude in the distraction condition than in the rumination condition.}\label{fig:everyone}
\end{figure}
